---
title: "ClassEval-intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ClassEval-intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This package provides tools for classification tasks including model training, evaluation metrics, cross-validation, and visualization.


## Example workflow

```{r example, echo=TRUE}
library(ClassEval)
# Load data
data(titanic_expanded)

# Train model
model <- train_logistic_model(Survived ~ Class + Sex, titanic_expanded)

# Predict
pred <- predict_model(model, titanic_expanded)

# Evaluate
accuracy_score(titanic_expanded$Survived, pred)

# Plot
plot_confusion_matrix(titanic_expanded$Survived, pred)

# Cross validation
k_fold_cv(Survived ~ Class + Sex, titanic_expanded)

# Compare models
compare_models(Survived ~ Class + Sex, titanic_expanded)
```


## Reflectioon

During the development of the ClassEval package, several important lessons and insights were gained:

1. Modular design improves code reusability

By separating functionalities into individual functions such as model training, prediction, evaluation, and visualization, the package becomes easier to maintain and extend. This modular approach avoids code duplication and enhances clarity.

2. Pipeline integration is essential in machine learning workflows

The package demonstrates a complete pipeline from model training to evaluation (train → predict → evaluate → visualize). This structured workflow reflects real-world data science practices.

3. Data preprocessing plays a critical role

Handling data types correctly is crucial. For example, converting labels to factors for SVM classification is necessary to avoid unintended regression behavior.

4. R-specific data type issues is important!

The conversion between factor, character, and numeric types can lead to subtle bugs. Proper handling of these conversions ensures correct model predictions and evaluation results.

5. Cross-validation improves model reliability

Implementing k-fold cross-validation provides a more robust estimate of model performance compared to a single train-test split, reducing variance and overfitting risk.

6. Visualization enhances interpretability

Using heatmaps to represent confusion matrices makes it easier to understand model performance compared to raw numerical outputs.

7. Leveraging existing libraries effectively

The use of packages such as ggplot2, e1071, and pROC demonstrates how combining existing tools can accelerate development while maintaining flexibility.

8. Automated testing ensures correctness and robustness

Writing unit tests using testthat helps verify that each function behaves as expected, reducing the risk of hidden bugs.

9. Consistent interface design improves usability

Designing a unified prediction interface (predict_model) for different models simplifies usage and enhances user experience.

10. Building an R package requires more than writing functions

Beyond coding, tasks such as documentation, namespace management, dataset integration, and vignette writing are essential parts of package development.

Overall, this project provided practical experience in building a structured and reusable data science toolkit in R.
